### 2017-10-30 manuscript.rmd
removed error messages from simmap, knitted new ms

In the final analyses, we sampled 1,071 genes to generate a supermatrix with 60% occupancy and a length of 378,468 amino acids. Two outgroup species, *Atolla vanhoeffeni* and *Aegina citrea*, were removed from the final supermatrix and phylogeny due to low gene occupancy (gene sampling of 20.8% and 14.5% respectively in a 50% occupancy matrix with 2,203 genes). ML analyses were conducted on the unpartitioned supermatrix using the WAG+Γ model of amino acid substitution, and bootstrap values were estimated using 1000 replicates. BI was conducted using two different CAT models, CAT-Poisson and CAT-GTR [@doi:10.1093/molbev/msh112]. Two independent MCMC chains were run under the CAT-GTR model, and four independent MCMC chains were run under the CAT-Poisson model. The CAT-GTR and CAT-poisson models did not converge after a long CPU time, and only the results from the CAT-poisson model are included here.

@@

Stochastic trait mapping:
```{r simmap_making, echo=F, message=F, warning=F}
#Make simmap objects
print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100) -> sex_sim
print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100) -> palpons_sim
print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100) -> tentilla_sim
print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100) -> tentilla_sim2
print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100) -> nectosome_sim
print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100) -> necto_pos_sim
print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100) -> necto_types_sim
print("SIMMAP Pneumatophore")
make.simmap(ultratree, pneuma, nsim = 100, pts=T) -> pneuma_sim
print("SIMMAP Bract Types")
make.simmap(ultratree, bracts, nsim = 100) -> bracts_sim
print("SIMMAP Habitat")
make.simmap(ultratree, vrange, nsim = 100) -> vrange_sim

@@

SIMMAP Sex distribution:
```{r sex, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap SEX
plotTree(ultratree, lwd = 4)
sex_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)
```

@@

SIMMAP Presence of palpons:
```{r palpons, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap PALPONS
plotTree(ultratree, lwd = 4)
palpons_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```

@@

SIMMAP Presence of tentilla:
```{r tentilla, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
tentilla_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)
```

@@

SIMMAP Presence of tentilla - *Physalia* corrected:
```{r tentilla2, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
tentilla_sim2 %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim2)
```

@@

SIMMAP Presence of Nectophores:
```{r nectosome, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap NECTOSOME
plotTree(ultratree, lwd = 4)
nectosome_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(nectosome_sim)
```

@@

SIMMAP Position of Nectosome:
```{r nectosome_position, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#SIMMAP NECTOSOME POSITION
plotTree(ultratree, lwd = 4)
necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green")
names(colors) = c("Dorsal", "No nectosome", "Ventral")
nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

SIMMAP Nectophore number and types:
```{r nectophore_number_types, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap NECTOPHORE TYPES
plotTree(ultratree, lwd = 4)
necto_types_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red", "green", "blue")
names(colors) = c("Multiple of one type", "None", "Two of one type", "Two of two types")
nodelabels(pie=(describe.simmap(necto_types_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

SIMMAP Presence of Pneumatophore:
```{r pneumatophore, echo=F, message=F, warning=F, fig.height=7, fig.width=12}
#Simmap PNEUMATOPHORE
plotTree(ultratree, lwd = 4)
pneuma_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nodelabels(pie=(describe.simmap(pneuma_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(pneuma_sim)
```

@@

SIMMAP Number of Bract types:
```{r bract_types, echo=F, fig.height=7, fig.width=12, message=F, warning=F}
#Simmap bract-types
plotTree(ultratree, lwd = 4)
bracts_sim %>% plotSimmap(lwd = 4, add = T) -> bract_sim_plot
#plot(bract_sim_plot[2])
colors = c("black", "red", "green3", "blue")
names(colors) = c("No bracts", "1", "2", "4")
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

SIMMAP Habitat:
```{r depth_zones, echo=F, fig.height=7, fig.width=12, message=F, warning=F}
#Simmap Vertical.Range
plotTree(ultratree, lwd = 4)
vrange_sim %>% plotSimmap(lwd = 4, add = T)
colors = c("black", "cyan", "blue", "green", "red")
names(colors) = c("Bathypelagic", "Surface", "Mesopelagic", "Epipelagic", "Deep benthic")
nodelabels(pie=(describe.simmap(vrange_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

>>>>

In the final analyses, we sampled 1,071 genes to generate a supermatrix with 60% occupancy and a length of 378,468 amino acids. Two outgroup species, *Atolla vanhoeffeni* and *Aegina citrea*, were removed from the final supermatrix and phylogeny due to low gene occupancy (gene sampling of 20.8% and 14.5% respectively in a 50% occupancy matrix with 2,203 genes). ML analyses were conducted on the unpartitioned supermatrix using the WAG+$\gamma$ model of amino acid substitution, and bootstrap values were estimated using 1000 replicates. BI was conducted using two different CAT models, CAT-Poisson and CAT-GTR [@doi:10.1093/molbev/msh112]. Two independent MCMC chains were run under the CAT-GTR model, and four independent MCMC chains were run under the CAT-Poisson model. The CAT-GTR and CAT-poisson models did not converge after a long CPU time, and only the results from the CAT-poisson model are included here.

@@

Stochastic trait mapping:
```{r simmap_making, echo=F, message=F, warning=F}
#Make simmap objects
print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100, message=FALSE) -> necto_types_sim
print("SIMMAP Pneumatophore")
make.simmap(ultratree, pneuma, nsim = 100, message=FALSE, pts=T) -> pneuma_sim
print("SIMMAP Bract Types")
make.simmap(ultratree, bracts, nsim = 100, message=FALSE) -> bracts_sim
print("SIMMAP Habitat")
make.simmap(ultratree, vrange, nsim = 100, message=FALSE) -> vrange_sim

@@

SIMMAP Sex distribution:
```{r sex, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(sex_sim)
```

@@

SIMMAP Presence of palpons:
```{r palpons, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap PALPONS
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(palpons_sim)
```

@@

SIMMAP Presence of tentilla:
```{r tentilla, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)
```

@@

SIMMAP Presence of tentilla - *Physalia* corrected:
```{r tentilla2, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap TENTILLA
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim2)
```

@@

SIMMAP Presence of Nectophores:
```{r nectosome, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap NECTOSOME
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(nectosome_sim)
```

@@

SIMMAP Position of Nectosome:
```{r nectosome_position, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#SIMMAP NECTOSOME POSITION
plotTree(ultratree, lwd = 4)
colors = c("black", "red", "green")
names(colors) = c("Dorsal", "No nectosome", "Ventral")
necto_pos_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

SIMMAP Nectophore number and types:
```{r nectophore_number_types, echo=F, message=F,fig.height=7, fig.width=12, warning=F}
#Simmap NECTOPHORE TYPES
plotTree(ultratree, lwd = 4)
colors = c("black", "red", "green", "blue")
names(colors) = c("Multiple of one type", "None", "Two of one type", "Two of two types")
necto_types_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(necto_types_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

SIMMAP Presence of Pneumatophore:
```{r pneumatophore, echo=F, message=F, warning=F, fig.height=7, fig.width=12}
#Simmap PNEUMATOPHORE
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
pneuma_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(pneuma_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(pneuma_sim)
```

@@

SIMMAP Number of Bract types:
```{r bract_types, echo=F, fig.height=7, fig.width=12, message=F, warning=F}
#Simmap bract-types
plotTree(ultratree, lwd = 4)
colors = c("black", "red", "green3", "blue")
names(colors) = c("No bracts", "1", "2", "4")
bracts_sim %>% plotSimmap(lwd = 4, add = T,colors=colors) -> bract_sim_plot
#plot(bract_sim_plot[2])
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

SIMMAP Habitat:
```{r depth_zones, echo=F, fig.height=7, fig.width=12, message=F, warning=F}
#Simmap Vertical.Range
plotTree(ultratree, lwd = 4)
colors = c("black", "cyan", "blue", "green", "red")
names(colors) = c("Bathypelagic", "Surface", "Mesopelagic", "Epipelagic", "Deep benthic")
vrange_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(vrange_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```
